## biorxiv

##### *Quickly search and get details about papers on the pre-print server [biorxiv.org](http://www.biorxiv.org) in R*

**Quick Start**

Currently the package is only available on github and installable via `devtools`
```{r install}
library(devtools)
install_github("emhart/biorxiv")
```

**Searching**

The search functionality comes from the general search form interface, so the search may not be at the granularity you desire without further parsing of results.

```{r searching}
bxCC <- bx_search("climate change",limit = 10)
summary(bxCC)
```

This will return a search results object that has the URL's for your search results.  If you want to get details about all your search results we can extract basic features like DOI, Authors, e-mails, title, abstract text, date as well as metrics on views and downloads.

```{r get details}
bxCCDetails <-  bx_extract(bxCC)

bxCCDetails[[1]]

```

There's also some basic plotting functionality that will allow you plot views and downloads

Plot views
```{r plotting views}
plot(bxCCDetails[[1]],type="abs")

```

Plot downloads
```{r plotting dl}
plot(bxCCDetails[[1]],type="dl")

```


