## biorxiv

*Quickly search and get details about papers on the pre-print server [biorxiv.org](http://www.biorxiv.org) in R*

**Quick Start**

Currently the package is only available on github and installable via `devtools`
```{r install,message=FALSE,warning=FALSE}
library(devtools)
install_github("emhart/biorxiv")
library(biorxiv)
```

**Searching**

The search functionality comes from the general search form interface, so the search may not be at the granularity you desire without further parsing of results.

```{r searching}
bxEco <- bx_search("Ecology",limit = 10)
summary(bxEco)
```

This will return a search results object that has the URL's for your search results.  If you want to get details about all your search results we can extract basic features like DOI, Authors, e-mails, title, abstract text, date as well as metrics on views and downloads.

```{r get details}
bxEcoDetails <-  bx_extract(bxEco)

bxEcoDetails[[1]]

```

There's also some basic plotting functionality that will allow you plot views and downloads

Plot views
```{r plotting views}
plot(bxEcoDetails[[1]],type="abs")

```

Plot downloads
```{r plotting dl}
plot(bxEcoDetails[[1]],type="dl")

```

Finally, you can easily download PDF's from all your search results.

```{r dl,eval=FALSE}
bx_download(bxEco,"~/biorxiv_pdfs")

```


